---
title: "Report on Happiness up to 2022"
author:
- familyname: Yang 
  othernames: Zhixiang
  email: zyan0056@student.monash.edu
  correspondingauthor: true
  qualifications:  EBS Honours Student
- familyname: Wang
  othernames: Yiqi
  email: ywan0684@studnet.monash.edu
  qualifications: Master of BA Student
- familyname: You
  othernames: Xintong
  email: xyou0004@student.monash.edu
  correspondingauthor: true
  qualifications: Master of BA Student
phone: (03) 9905 2478
department: Department of\newline Econometrics &\newline Business Statistics
organization: Group 07 ETC5513
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  monash::report:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---


section YIQI WANG

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      message = FALSE, 
                      warning = FALSE,
                      comment = NA,
                      include = FALSE)
```

# Load Packages

```{r}
library(tidyverse)
library(gganimate)
library(GGally)
```


# Read Data

```{r}
data2015 <- read_csv('Data/2015.csv')
data2016 <- read_csv('Data/2016.csv')
data2017 <- read_csv('Data/2017.csv')
data2018 <- read_csv('Data/2018.csv')
data2019 <- read_csv('Data/2019.csv')
data2020 <- read_csv('Data/2020.csv')
data2021 <- read_csv('Data/2021.csv')
data2022 <- read_csv('Data/2022.csv')
```



```{r dataPreparation}
data2015 <- data2015 %>% 
  select(Country,Region,`Happiness Score`,
         `Economy (GDP per Capita)`,
         `Health (Life Expectancy)`,
         Freedom) %>% 
  rename('Happiness_Score' = 'Happiness Score',
         'Economy' = 'Economy (GDP per Capita)',
         'Health' = 'Health (Life Expectancy)') %>% 
  mutate(Year = 2015)

data2016 <- data2016 %>% 
  select(Country,`Happiness Score`,
         `Economy (GDP per Capita)`,
         `Health (Life Expectancy)`,
         Freedom) %>% 
  rename('Happiness_Score' = 'Happiness Score',
         'Economy' = 'Economy (GDP per Capita)',
         'Health' = 'Health (Life Expectancy)') %>% 
  mutate(Year = 2016)

data2017 <- data2017 %>% 
  select(Country,Happiness.Score,
         Economy..GDP.per.Capita.,
         Health..Life.Expectancy.,
         Freedom) %>% 
  rename('Happiness_Score' = 'Happiness.Score',
         'Economy' = 'Economy..GDP.per.Capita.',
         'Health' = 'Health..Life.Expectancy.') %>% 
  mutate(Year = 2017)

data2018 <- data2018 %>% 
  select(`Country or region`,
         Score,
         `GDP per capita`,
         `Healthy life expectancy`,
         `Freedom to make life choices`) %>%
  rename('Country' = 'Country or region',
         'Happiness_Score' = 'Score',
         'Economy' = 'GDP per capita',
         'Health' = 'Healthy life expectancy',
         'Freedom' = 'Freedom to make life choices') %>% 
  mutate(Year = 2018)

data2019 <- data2019 %>% 
  select(`Country or region`,
         Score,
         `GDP per capita`,
         `Healthy life expectancy`,
         `Freedom to make life choices`) %>%
  rename('Country' = 'Country or region',
         'Happiness_Score' = 'Score',
         'Economy' = 'GDP per capita',
         'Health' = 'Healthy life expectancy',
         'Freedom' = 'Freedom to make life choices') %>% 
  mutate(Year = 2019)

data2020 <- data2020 %>% 
  select(`Country name`,
         `Ladder score`,
         `Explained by: Log GDP per capita`,
         `Explained by: Healthy life expectancy`,
         `Freedom to make life choices`) %>%
  rename('Country' = 'Country name',
         'Happiness_Score' = 'Ladder score',
         'Economy' = 'Explained by: Log GDP per capita',
         'Health' = 'Explained by: Healthy life expectancy',
         'Freedom' = 'Freedom to make life choices') %>% 
  mutate(Year = 2020)

data2021 <- data2021 %>% 
  select(`Country name`,
         `Ladder score`,
         `Explained by: Log GDP per capita`,
         `Explained by: Healthy life expectancy`,
         `Freedom to make life choices`) %>%
  rename('Country' = 'Country name',
         'Happiness_Score' = 'Ladder score',
         'Economy' = 'Explained by: Log GDP per capita',
         'Health' = 'Explained by: Healthy life expectancy',
         'Freedom' = 'Freedom to make life choices') %>% 
  mutate(Year = 2021)

data2022 <- data2022 %>% 
  select(Country,
         `Happiness score`,
         `Explained by: GDP per capita`,
         `Explained by: Healthy life expectancy`,
         `Explained by: Freedom to make life choices`) %>%
  rename('Happiness_Score' = 'Happiness score',
         'Economy' = 'Explained by: GDP per capita',
         'Health' = 'Explained by: Healthy life expectancy',
         'Freedom' = 'Explained by: Freedom to make life choices') %>% 
  mutate(Year = 2022,
         Happiness_Score = Happiness_Score/1000,
         Economy = str_replace(Economy,',','.') %>% as.numeric(),
         Health = str_replace(Health,',','.') %>% as.numeric(),
         Freedom = str_replace(Freedom,',','.') %>% as.numeric())
```


```{r dataPreparation2}
area <- data2015 %>% 
  select(Country,Region)

data2016 <- area %>% 
  left_join(data2016,by = 'Country')

data2017 <- area %>% 
  left_join(data2017,by = 'Country')

data2018 <- area %>% 
  left_join(data2018,by = 'Country')

data2019 <- area %>% 
  left_join(data2019,by = 'Country')

data2020 <- area %>% 
  left_join(data2020,by = 'Country')

data2021 <- area %>% 
  left_join(data2021,by = 'Country')

data2022 <- area %>% 
  left_join(data2022,by = 'Country')
```

```{r data_Preparation}
data1 <- bind_rows(data2015,data2016,data2017,data2018,
                 data2019,data2020,data2021,data2022)
```


### Introduction
This report explores two research questions in the context of the development of world happiness from 2015 to 2022 and related factors. The first is to study the trends of happiness score represented by region between 2015 and 2022, and thus lead to the relationship and impact of annual health and economic status on happiness score.


### The development of the World Happiness 

@helliwell2012state show with the continuous progress of human society, the happiness index has become an important standard for measuring the family, and people have also begun to study issues related to the happiness index. Since the happiness index is related to many factors of a family, it will also affect the The whole world. Therefore, this part will start with two research questions to explore the happiness index of the world.


### Data preparation and introduction
 
Our data comes from kaggle, which is a report of the World Happiness Index for the period 2015 to 2022, which contains variables for a number of factors such as countries, regions, happiness score, economies, health, freedom, etc. Combined with my research questions, I consolidated the datasets for each year into a dataset of data1, and the variables I needed to use were year, region, happiness score, economy, and health.

## Research questions

+ How will happiness trends change between 2015 to 2022 in different regions? 

+ What is the relationship between economic situation and health status with the happiness score? 






### the relationship between economic situation and health status with the happiness in 2015-2022

People's understanding of happiness is inseparable from their own living conditions, so in this report, we also studied the relationship between happiness and economic and health status.


From the figure \@ref(fig:VS), we can find that there is a positive correlation between economic status, health status and well-being from 2015 to 2022. The better the economic status and health status, the stronger the people's well-being.


From 2015 to 2022, the influence of the economic status on the happiness score is getting lower and lower, and the influence of the health on the happiness score has increased significantly. From 2017 to 2018, the influence of economic on happiness score increased slightly, while the influence of health  on happiness score decreased slightly during this period.





```{r table,cache=TRUE}
table1 %>% 
  knitr::kable('latex', 
               digits = 3, 
               booktabs = TRUE, 
               caption = "A linear relationship between economic status and health status with happiness index each year")%>%
  kableExtra::kable_styling(latex_options = "striped")
```


### Conclusions

Through our exploration of two research questions, we found that in economically developed countries, people's happiness is also higher, while people's happiness in economically backward areas will also be lower; and with the continuous progress of society, people's happiness comes from the impact of health, especially in the stage of covid-19. In general, some European countries and some developed countries have better welfare and medical security for their own developed economies, and people's happiness is also very high. On the contrary, in some economically poor areas, their welfare security is also poor, which also makes the happiness of the people not high.



